### 2009-12-16 doc/tech_doc/a-rex/arex_tech_doc.tex
gm-jobs -s switch ported from ARC0 to ARC1 with proper documentation update

\begin{itemize}
\item \textit{gm-jobs} -- prints a list of jobs available on the cluster
and the number of jobs in each state.\\
\hspace*{0.5cm}gm-jobs {[}-h] {[}-l] {[}-u uid] {[}-U name] {[}-c conf\_file] {[}-d control\_dir]\\
\hspace*{0.5cm}-h -- print short help,\\
\hspace*{0.5cm}-l -- print more information about each job,\\
\hspace*{0.5cm}-u -- pretend utility is run by user with id \emph{uid},\\
\hspace*{0.5cm}-U -- pretend utility is run by user with name \emph{name},\\
\hspace*{0.5cm}-c -- use specified configuration file,\\
\hspace*{0.5cm}-d -- read information from specified control dir.
\end{itemize}

@@

If VOMS is not supported, the \emph{dn} scheme is the only option that
should be used, as using a VOMS-based scheme will lead to all jobs
being assigned to the default share.

>>>>

\begin{itemize}
\item \textit{gm-jobs} -- prints a list of jobs available on the cluster
and the number of jobs in each state.\\
\hspace*{0.5cm}gm-jobs {[}-h] {[}-s] {[}-l] {[}-u uid] {[}-U name] {[}-c conf\_file] {[}-d control\_dir]\\
\hspace*{0.5cm}-h -- print short help,\\
\hspace*{0.5cm}-s -- print summary of jobs in each transfer share,\\
\hspace*{0.5cm}-l -- print more information about each job,\\
\hspace*{0.5cm}-u -- pretend utility is run by user with id \emph{uid},\\
\hspace*{0.5cm}-U -- pretend utility is run by user with name \emph{name},\\
\hspace*{0.5cm}-c -- use specified configuration file,\\
\hspace*{0.5cm}-d -- read information from specified control dir.
\end{itemize}

@@

If VOMS is not supported, the \emph{dn} scheme is the only option that
should be used, as using a VOMS-based scheme will lead to all jobs
being assigned to the default share. The current number of jobs
processing and pending processing for each share can be seen with the
command \emph{gm-jobs -s}.
